Distributed Ethereum Web Browser Mining\thanks{Supported by organization x.}

### 2018-03-22 paper/paper.tex
latest version of paper

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt, conference, compsocconf]{IEEEtran}
% Add the compsocconf option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

\usepackage{float}
\usepackage{graphicx}
\usepackage{balance}
\RequirePackageWithOptions{multicol}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

\usepackage{color}
\newcommand{\trishita}[1]{{\color{magenta}\bfseries[Trishita: #1]}}
\newcommand{\dennis}[1]{{\color{cyan}\bfseries[Dennis: #1]}}
% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

\usepackage{amsmath}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Distributed Web Browser Mining for Ethereum}

% author names and affiliations
% use a multiple column layout for up to two different
% affiliations

\author{\IEEEauthorblockN{
Trishita Tiwari\IEEEauthorrefmark{1}
David Starobinski\IEEEauthorrefmark{2}
Ari Trachtenberg\IEEEauthorrefmark{3}
}
\IEEEauthorblockA{Department of Electrical and Computer Engineering,
Boston University\\
Boston, MA, 02215\\
Email: 
\IEEEauthorrefmark{1}trtiwari@bu.edu
\IEEEauthorrefmark{2}staro@bu.edu
\IEEEauthorrefmark{3}trachten@bu.edu
}}
\maketitle

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
% \maketitle

\begin{abstract}

Given the seemingly endless growing popularity of crypto-currencies, there is an increasing interest in different mining possibilities. This paper proposes a web browser based mining implementation for Ethereum implemented both in JavaScript and WebAssembly to perform the necessary Proof-of-Work (PoW) computations to mine the Ethereum blockchain. We explore a variety of techniques to distribute the inherently memory and memory intensive PoW of Ethereum over multiple browser-based clients that have limited resources. We obtain the best results with the WebAssembly implementation, with hash rates reaching upto X hashes/second, which, as we demonstrate, is merely X\% slower than a native miner that uses the same algorithm for mining. We show that this solution is practical for a variety of purposes, such as web content monetization, web based authentication rate limiting and private Ethereum networks.

%Given the increasing need of effective ways to monetize web content and the growing popularity of crypto-currencies, we propose a new implementation of a distributed miner using web browsers. We implement this for the Ethereum crypto-currency, which shows that the use of web browsers is inefficient if the cryptocurrency requires large amount of storage for mining. However, we believe that such an approach can have merit depending on the crypto-currency that is being mined.

\end{abstract}

\begin{IEEEkeywords}
crypto-currency, Ethereum, distributed computing, mining
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
In today's world, crypto-currencies are gaining more and more traction as a viable form of currency. As such, people have been looking for efficient ways to mine the numerous crypto-currencies available. While much of these efforts have included creating new hardware, there has been considerable work done in re-using existing infrastructure in smarter ways to increase performance. One such effort is seen in using web browser as a platform for distributed computing ~\cite{Cushing}, and more recently, specifically for distributed crypto-currency mining ~\cite{coinhive}. In this work, we propose approaches to mine Ethereum, a popular crypto-currency, in a distributed fashion through web browsers. Our approach can be used for a variety of purposes, outlined as follows: 
\begin{enumerate}

\item \textbf{Web Content Monetization}: With the growth in global Internet usage, websites have become a lucrative way for people to earn monetary profit. As a result, new methods of monetizing electronic content have surfaced with time. While some are more successful than others, all of them have issues associated with them. For instance, selling advertisement space is now resulting in declining revenue \cite{decliningRevenue} for website owners due to the advent of new technologies such as AdBlock \cite{Adblock}, Brave Browser \cite{BraveBrowser}, etc. In addition, too many advertisements also tend to increase the loading time for web-pages. Moreover, such advertisements are sometimes not placed correctly and cover the contents of the website. Thus, this approach does not provide good user experience. Another approach involves subscriptions, however, it is not very successful. Indeed, as this study finds, users are becoming increasingly unlikely to pay for content \cite{noSubscriptions}. Website owners also use pay-per-click Advertising, however an approach often leads to the content being split over an excessive number of pages, thereby leading to consumer frustration \cite{payPerClick}. Thus, we see that each approach has its own issues, be it with  with website owners or clients. Hence, it is important to strike a balance and create a solution that would be able to benefit both parties. Our web-based miner would solve this situation as it does not 
\item \textbf{Web-Authentication Rate Limiting}: Brute forcing web login pages is becoming an all too common issue ~\cite{webLoginBruteForce}, and the way website owners mitigate this issue is by locking out a user for a certain amount of time after a fixed number of unsuccessful login attempts. While this approach works in theory, in today's fast-paced world, users tend to dislike waiting for even a few seconds ~\cite{usersDislikeWaiting}. Another solution to this problem involves embedding a Proof-of-Work (PoW) computation in the web page that the user's browser needs to successfully solve in order to be able to login. Our implementation uses the Ethereum PoW, which is extremely feasible for legitimate users attempting to login, but will thwart any attacker that attempts to brute force the login. Furthermore, the difficulty of the PoW can be tuned to obtain a balance between user experience and security. 
\item \textbf{Website usage tracking}: Website advertising sponsors decide on the remuneration for a website by inspecting the logs of the web servers in order to deduce how much traffic the site receives. However, it is well known that these logs can be easily manipulated by the website owner in order to generate the impression of a large amount of traffic ~\cite{webLogsManipulation}. Our web miner could solve these issues as it has this unique property of a direct correlation between a users hashrate and the time spent on the website (i.e., the longer the user spends on the web page, better the hashrate gets). Hence, our miner can be embedded within advertisements and allow advertisers to directly extrapolate how much traffic the website gets just by extrapolating from the average hash rate.
\item \textbf{Private Ethereum networks}: Ethereum is an extremely flexible currency in the sense that it allows for private coin networks -- i.e., networks that do not on mine the actual, public Ethereum block-chain, but rather on private (and often smaller) instances of the crypto-currency. Our browser miner can be used on any such private network to serve the network owner whatever he/she wishes to implement with the mining PoW.
\end{enumerate}

@@

\section{Outline}
The remainder of the paper is organized as follows. In Section 5 we present a detailed description of the Ethereum mining algorithm and the current state of Ethereum. Section 6 describes the Architecture of our implementation of the Distributed Web Browser Miner. Section 7 goes over the challenges that we have dealt with during our implementation and their effect on the project. Section 8 examines the results of our solution and compares it to current mining data to evaluate the efficacy of our work. Finally, in Section 9 we lay out possible future work, and in Section 10 provide conclusions and insight on the project.

% \item Affiliate Marketing: Unlike pay-per-click advertisements, such marketing might not cause inconvenience to users. However, it sometimes leads to ethically questionable situations when users are not able to distinguish when the website owner is advertising a product versus when the owner truly endorses it without monetary incentive \cite{celebEndorse}.

% \item Donations: While donations are perhaps the most benign of all approaches, they lead to unsteady revenue for the website owner.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)

\section{Background}
% \subsection{Distributed Web Browser Computing}
% One of the core concepts that this research is based on is the use of web browsers to perform computations; in our case that computation is the act of mining crypto-currency. First, we need to define the idea of distributed computing. Distributed computing is a network of computers that are working together to achieve a single goal. Web browser computing is a subset of distributed computing. In this scenario, the web browsers on the client machines are the workers. The use of web browsers for computation has come to light in the past 15-20 years because of improvements the \verb|JavaScript| engine ~\cite{Cushing}. In fact, the advent of powerful frameworks such as \verb|WebAssembly| are further closing down the gaps between web browser computations and native programs.

% To be able to implement an effective distributed system, each of the ``workers'' must have a way to communicate effectively with each other. There are two ways this is accomplished. One approach is to follow a server-client model in which there is a central server machine and all other machines are the clients. The clients speak to the server and the server can relay information from one client to another or broadcast information to all clients. The other way to have communication is a peer-to-peer model where all machines are aware of each other and can talk directly. When it comes to browsers, however, the only logical way to pass data is through the server-client architecture because web browsers are not created to perform peer-to-peer communication. So with that in mind, distributed web browser computing systems typically have a structure with a central server which distributes tasks to each web browser it is connected to. In general, these tasks are very small because there is no guarantee that the browser will be open for a sustained period of time, i.e. a user moves away from the necessary website or closes the browser altogether. Furthermore, the tasks must also not consume too many resources of the user, as such browser based computation would ruin user experience. Given these two constraints, we propose two approaches to distribute ethereum mining in over web browsers.

\subsection{Ethereum}
\trishita{Not sure if I need this paragraph, since I think the readers will probably be familiar with what crypto-curriencies are}
Ethereum is a crypto-currency that was released in July 2015 by Vitalik Buterin, Gavin Wood and Jeffrey Wilcke. Like most crypto-currencies, it too is backed by a distributed block-chain, each block of which holds transactions for that particular block-chain. This block chain is operated on by the Ethereum Virtual Machine (EVM) ~\cite{EVM}, which, unlike Bitcoin Script, is Turing Complete ~\cite{turingComplete}. Furthermore, this currency is also a Proof-of-Work based currency, which means that the new blocks are appended to the block-chain through a process called ``mining''. Mining involves a race amongst miners to solve a Proof-of-Work puzzle (usually an energy intensive computation), the winner of which gets to have his block appended to the block-chain. The winner also receives a payout, which acts as an incentive to mine. This process of mining is essential to deciding the order in which transactions are appended to the inherently decentralized block-chain, thereby stabilizing the chain. Ethereum uses Ethash as its Proof-of-Work (PoW) algorithm, which is explained in detail below.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{float}
\usepackage{graphicx}
\usepackage{balance}
\usepackage{color}
\usepackage{amsmath}
\newcommand{\trishita}[1]{{\color{magenta}\bfseries[Trishita: #1]}}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\begin{document}
%
\title{Distributed Ethereum Web Browser Mining\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Trishita Tiwari\orcidID{0000-1111-2222-3333} \and
David Starobinski\orcidID{1111-2222-3333-4444} \and
Ari Trachtenberg\orcidID{2222--3333-4444-5555}}
%
\authorrunning{T. Tiwari et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Boston University, Department of Electrical and Computer Engineering, Boston, MA 02215, USA \\
\email{\{trtiwari,staro,trachten\}@bu.edu}}
%
\maketitle             
%
\begin{abstract}
Given the seemingly endless growing popularity of crypto-currencies, there is an increasing interest in different mining possibilities. This paper proposes a web browser based mining implementation for Ethereum implemented both in JavaScript and WebAssembly to perform the necessary Proof-of-Work (PoW) computations to mine the Ethereum blockchain. We explore a variety of techniques to distribute the inherently memory and memory intensive PoW of Ethereum over multiple browser-based clients that have limited resources. We obtain the best results with the WebAssembly implementation, with hash rates reaching upto X H/s, which, as we demonstrate, is merely X\% slower than a native miner that uses the same algorithm for mining. We show that this solution is practical for a variety of purposes, such as web content monetization, web based authentication rate limiting and private Ethereum networks.

\keywords{crypto-currency \and Ethereum \and distributed computing \and web-browser computing \and mining}
\end{abstract}
%
%
%
\section{Introduction}
In today's world, crypto-currencies are gaining more and more traction as a viable form of currency. As such, people have been looking for efficient ways to mine the numerous crypto-currencies available. While much of these efforts have included creating new hardware, there has been considerable work done in re-using existing infrastructure in smarter ways to increase performance. One such effort is seen in using web browser as a platform for distributed computing ~\cite{Cushing}, and more recently, specifically for distributed crypto-currency mining ~\cite{coinhive}. In this work, we propose approaches to mine Ethereum, a popular crypto-currency, in a distributed fashion through web browsers. Our approach can be used for a variety of purposes, outlined as follows: 
\begin{enumerate}

\item \textbf{Web Content Monetization}: With the growth in global Internet usage, websites have become a lucrative way for people to earn monetary profit. As a result, new methods of monetizing electronic content have surfaced with time. While some are more successful than others, all of them have issues associated with them. For instance, selling advertisement space is now resulting in declining revenue \cite{decliningRevenue} for website owners due to the advent of new technologies such as AdBlock \cite{Adblock}, Brave Browser \cite{BraveBrowser}, etc. In addition, too many advertisements also tend to increase the loading time for web-pages. Moreover, such advertisements are sometimes not placed correctly and cover the contents of the website. Thus, this approach does not provide good user experience. 
% Another approach involves subscriptions, however, it is not very successful. Indeed, as this study finds, users are becoming increasingly unlikely to pay for content \cite{noSubscriptions}. Website owners also use pay-per-click Advertising, however an approach often leads to the content being split over an excessive number of pages, thereby leading to consumer frustration \cite{payPerClick}. Thus, we see that each approach has its own issues, be it with  with website owners or clients. Hence, it is important to strike a balance and create a solution that would be able to benefit both parties. Our web-based miner would solve this situation as it does not 
\item \textbf{Web-Authentication Rate Limiting}: Brute forcing web login pages is becoming an all too common issue ~\cite{webLoginBruteForce}, and the way website owners mitigate this issue is by locking out a user for a certain amount of time after a fixed number of unsuccessful login attempts. While this approach works in theory, in today's fast-paced world, users tend to dislike waiting for even a few seconds ~\cite{usersDislikeWaiting}. Another solution to this problem involves embedding a Proof-of-Work (PoW) computation in the web page that the user's browser needs to successfully solve in order to be able to login. Our implementation uses the Ethereum PoW, which is extremely feasible for legitimate users attempting to login, but will thwart any attacker that attempts to brute force the login. Furthermore, the difficulty of the PoW can be tuned to obtain a balance between user experience and security. 
\item \textbf{Website usage tracking}: Website advertising sponsors decide on the remuneration for a website by inspecting the logs of the web servers in order to deduce how much traffic the site receives. However, it is well known that these logs can be easily manipulated by the website owner in order to generate the impression of a large amount of traffic ~\cite{webLogsManipulation}. Our web miner could solve these issues as it has this unique property of a direct correlation between a users hashrate and the time spent on the website (i.e., the longer the user spends on the web page, better the hashrate gets). Hence, our miner can be embedded within advertisements and allow advertisers to directly extrapolate how much traffic the website gets just by extrapolating from the average hash rate.
\item \textbf{Private Ethereum networks}: Ethereum is an extremely flexible currency in the sense that it allows for private coin networks -- i.e., networks that do not on mine the actual, public Ethereum block-chain, but rather on private (and often smaller) instances of the crypto-currency. Our browser miner can be used on any such private network to serve the network owner whatever he/she wishes to implement with the mining PoW.
\end{enumerate}

@@

% \section{Outline}
% The remainder of the paper is organized as follows. In Section 5 we present a detailed description of the Ethereum mining algorithm and the current state of Ethereum. Section 6 describes the Architecture of our implementation of the Distributed Web Browser Miner. Section 7 goes over the challenges that we have dealt with during our implementation and their effect on the project. Section 8 examines the results of our solution and compares it to current mining data to evaluate the efficacy of our work. Finally, in Section 9 we lay out possible future work, and in Section 10 provide conclusions and insight on the project.

\section{Background}
% \subsection{Ethereum}
% \trishita{Not sure if I need this paragraph, since I think the readers will probably be familiar with what crypto-curriencies are}
Ethereum is a crypto-currency that was released in July 2015 by Vitalik Buterin, Gavin Wood and Jeffrey Wilcke. Ethereum uses the Ethash algorithm for its PoW, which is discussed below in detail. 
% Like most crypto-currencies, it too is backed by a distributed block-chain, each block of which holds transactions for that particular block-chain. This block chain is operated on by the Ethereum Virtual Machine (EVM) ~\cite{EVM}, which, unlike Bitcoin Script, is Turing Complete ~\cite{turingComplete}. Furthermore, this currency is also a Proof-of-Work based currency, which means that the new blocks are appended to the block-chain through a process called ``mining''. Mining involves a race amongst miners to solve a Proof-of-Work puzzle (usually an energy intensive computation), the winner of which gets to have his block appended to the block-chain. The winner also receives a payout, which acts as an incentive to mine. This process of mining is essential to deciding the order in which transactions are appended to the inherently decentralized block-chain, thereby stabilizing the chain. Ethereum uses Ethash as its Proof-of-Work (PoW) algorithm, which is explained in detail below.

\subsection{Ethash}
Ethash is the PoW used for mining blocks in Ethereum. Derived from the Dagger and Hashimoto algorithms ~\cite{dagger-hashimoto}, Ethash operates by first generating a 256 bit seed. This seed is different for every epoch (30,000 blocks). For the first epoch it is the Keccak-256 hash of a series of 32 bytes of zeros. For every other epoch it is always the Keccak-256 hash of the previous seed hash. This seed is then used to compute a pseudo-random cache. The cache production process involves using the seed hash to first sequentially filling up X bytes of memory (size of the cache), then performing Y passes of the RandMemoHash algorithm ~\cite{randmemohash}. This transforms the initial cache to give us the final value for the cache. This cache is simply an array 4 byte integers ~\cite{Ethmining}. Lightweight clients may use this cache for verification, while full node clients can use it to calculate a DAG (Directed Acyclic Graph) file. Essentially, each node in the DAG is generated by combining data from 256 pseudorandomly selected cache nodes and hashing them together. This process is repeated to generate all nodes in the DAG. Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128B wide ``Mix'' (another byte array). The Mix is then used to fetch a specific slice of the DAG from memory. (Each slice is 512 bits long, or 16 4 byte integers) After this, the Mix is updated with the fetched part of the DAG. Then, this updated Mix is used to fetch a new part of the DAG. This process of sequentially fetching parts of the DAG is repeated 64 times, and the final value of the Mix is put through a transformation to obtain a 32 byte digest. This digest is then compared to the threshold, and if it is lesser than it, the nonce is valid and the block is successfully mined and can be broadcast to the network. However, if the digest is greater than the threshold, the nonce was unsuccessful, and the entire process must be repeated with a new nonce ~\cite{Ethmining}. This procedure for mining is depicted in figure ~\ref{fig:ethash}. It is important to note that the parts of the DAG that are used to compute the hash for a particular block depend on the nonce used, hence no way to pre-determine which parts will be useful to have in memory. Hence this forces miners to store entire DAG in memory, making mining ``Memory Hard''. This is intended to even the playing field, as ASIC miners no longer have any advantage as they do for Bitcoin. GPU miners, however, do have an advantage, normally having hashrates of over 10 times that of a CPU miner.
While mining is memory intensive, verification is relatively lightweight. This is because of the property that each ``slice'' in the DAG depends on a set of pseudo-randomly selected items from the Cache. Hence, the Cache is used to regenerate only the specific slices of the DAG that are needed to recalculate the hash for the particular nonce. And so only the Cache needs to be stored by clients that just perform verification. We use this property of being able to generate the parts of the DAG as needed to our advantage in order to alleviate some of the memory and network bandwidth restrictions that browsers typically face.

As time goes on, mining Ethereum becomes more and more difficult, as the size of the DAG and Cache used for the Ethereum increases every Epoch. Currently the DAG is more than 2GB in size, causing many GPU miners with cards of 2GB of memory to suffer in terms of hashrate. 
% The Proof-of-Work difficulty and total hashrate of the network has been steadily increasing over time, with the current difficulty at 1612.737TH and the respective hashrate at 109.138TH/s ~\cite{etherscan}. This reflects the design of mining one block approximately every 12 seconds. 
% As for mining rewards, the reward for mining a block has gone from 5 Ether to 3 ether, though the difficulty has significantly decreased, both due to the Byzantium fork.
